Where Do Population III Stars Form? The Effects of Radiative Feedback and Self-Shielding on the Host Halo Mass Distribution

### 2019-05-13 paper.tex
Okay, one more tiny adjustment to the abstract

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars. \hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature. In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}. We investigate the distribution of host halo masses and its relationship to the Lyman-Werner background intensity. In our simulation above a redshift of 11.5, the mean halo mass is time-independent and $7.7 \times 10^{5} M_{\odot}$. Afterwards, it steadily rises to a mean value of $3.7 \times 10^{6} M_{\odot}$, due to the increased LW background coming from a massive galaxy actively forming stars. Compared to the literature, our halos form Pop III stars at much lower masses due tot eh inclusion of \hh{} self-shielding. Most halos form multiple Population III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. We also find that a few halos do form stars in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$. Our results suggest that Population III star formation may be less affected by Lyman-Werner radiation feedback than previously thought and that Population III multiple systems are common. 
\end{abstract}{}

>>>>

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars. \hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature. In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}. We investigate the distribution of host halo masses and its relationship to the LW background intensity. In our simulation above a redshift of 11.5, the mean halo mass is time-independent and $7.7 \times 10^{5} M_{\odot}$. Afterwards, it steadily rises to a mean value of $3.7 \times 10^{6} M_{\odot}$, due to the increased LW background coming from a massive galaxy actively forming stars. Compared to the literature, our halos form Pop III stars at much lower masses due to the inclusion of \hh{} self-shielding. Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. We also find that a few halos do form stars in a high LW radiation field with values up to ~50 J$_{21}$. Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common. 
\end{abstract}{}
